Understanding the Ising CFT

### 2021-06-09 Strings2020/strings5/strings5.tex
Fix $tex_program handling in compile.sh
Clean up preambles, update templates
Tweak strings homework
Add comments on string partition function & more

%%% ID: sensitive, do NOT publish!
\InputIfFileExists{../id.tex}{}{}

\newcommand{\oppower}[2]{\mop{{#1}^{#2}}\!}
\newcommand{\sqsinh}{\oppower{\sinh}{2}}
\newcommand{\sqcosh}{\oppower{\cosh}{2}}

\newcommand{\Vir}{\mathbf{V}\mfrak{ir}}
\newcommand{\zbar}{\bar{z}}
\usepackage{tikz-feynman,cancel}

@@

	Using the expressions in (a), we find that $L_0$ action on a state $\ket{\psi}$ created by $\alpha_{-l},\tilde{\alpha}_{-l}$ yields the sum of occupation numbers $N_l$ weighted by $l$:
	\begin{equation}
		L_0 \ket{\psi}
		= \pqty{
				\frac{\alpha'k_L^2}{4}
				+ \sum_{l > 0} l\cdot N_l
			} \ket{\psi}
	\end{equation}
	With $c = \tilde{c} = 1$, we obtain:
	\begin{equation}
	\begin{aligned}
		Z(\tau)
		&= (q\bar{q})^{-\frac{1}{24}}
			\sum_{n,w}
				e^{
					- 2\pi \tau_2
					\alpha'\frac{k_L^2 + k_R^2}{4}
				}
				e^{
					2\pi i \tau_1
					\alpha'\frac{k_L^2 - k_R^2}{4}
				}
			\sum_{(N_l),(\tilde{N}_l)}
				q^{
					\,\sum\limits_{l>0}  l\cdot N_l
				}
				\bar{q}^{
					\,\sum\limits_{l>0}  l\cdot \tilde{N}_l
				} \\
		&= (q\bar{q})^{-\frac{1}{24}}
			\sum_{n,w}
				e^{
					- \pi \tau_2 \pqty{
						\frac{\alpha'n^2}{R^2}
						+ \frac{w^2 R^2}{\alpha'}
					}
					+ 2\pi i \tau_1 nw
				}
			\sum_{(N_l),(\tilde{N}_l)} \prod_{l>0}
				q^{l\cdot N_l}
				\bar{q}^{\,l\cdot \tilde{N}_l} \\
		&= \abs{\eta(\tau)}^{-2}
			\sum_{n,w}
				e^{
					- \pi \tau_2 \pqty{
						\frac{\alpha'n^2}{R^2}
						+ \frac{w^2 R^2}{\alpha'}
					}
					+ 2\pi i \tau_1 nw
				}
	\end{aligned}
	\end{equation}
	We've simplified the contributions from the oscillator modes using $\eta(\tau)$, since they are identical to the oscillator contributions of the non-compact $X\in\mbb{R}^1$:
	\begin{equation}
	\begin{aligned}
		(q\bar{q})^{-\frac{1}{24}}\!\!\!\!\!
		\sum_{(N_l),(\tilde{N}_l)} \prod_{l>0}
			q^{l\cdot N_l}
			\bar{q}^{\,l\cdot \tilde{N}_l}
		&= (q\bar{q})^{-\frac{1}{24}}
			\prod_{l>0} \sum_{N_l,\tilde{N}_l = 0}^\infty
				q^{l\cdot N_l}
				\bar{q}^{\,l\cdot \tilde{N}_l} \\
		&= (q\bar{q})^{-\frac{1}{24}}
			\prod_{l>0}
				\frac{1}{1 - q^l}
				\frac{1}{1 - \bar{q}^{\,l}}
		= \abs{\eta(\tau)}^{-2}
	\end{aligned}
	\end{equation}

@@

	The sum, on the other hand, is naturally invariant under $T\colon \tau \mapsto \tau + 1$, by making a change of variables $m \mapsto m + w$. It is also invariant under $S\colon \tau \mapsto -1/\tau$ with $m \mapsto −w, w \mapsto m$\,\footnote{
		Reference: \textit{Polchinski}. 
	}. Therefore, $Z(\tau)$ is modular invariant.

@@

	For the second term, note that:
	\begin{equation}
		r\colon\ %
				\ket{(N_l),(\tilde{N}_l);n,w}
			\longmapsto (−1)^{\sum_l (N_l + \tilde{N}_l)}
				\ket{(N_l),(\tilde{N}_l);-n,-w}
	\end{equation}
	In particular, it reverses $n,w$, hence $r$ insertion gives vanishing amplitude unless $n = w = 0$; the summation is very much similar to the $Z_{S^1}$ case, i.e. we have:
	\begin{equation}
	\begin{aligned}
		\frac{1}{2} \Tr_{S^1} \pqty\Big{
			r\,
			q^{L_0 - \tfrac{c}{24}}\,
			\bar{q}^{\tilde{L}_0 - \tfrac{\tilde{c}}{24}}
		}
		&= \frac{1}{2}\,(q\bar{q})^{-\frac{1}{24}}
			\prod_{l>0} \sum_{N_l,\tilde{N}_l = 0}^\infty
				(−1)^{N_l + \tilde{N}_l}
				q^{l\cdot N_l}
				\bar{q}^{\,l\cdot \tilde{N}_l} \\
		&= \frac{1}{2}\,(q\bar{q})^{-\frac{1}{24}}
			\prod_{l>0}
				\frac{1}{1 - (-q^l)}
				\frac{1}{1 - (-\bar{q}^{\,l})}
		= \abs{\frac{\eta(\tau)}{\theta_2(\tau)}}
	\end{aligned}
	\end{equation}
	Where we've used the fact that\footnote{
		Reference: Blumenhagen \& Plauschinn, \textit{Introduction to CFT}, and also \textit{Polchinski}. 
	}: $
		q^{-\frac{1}{24}}
		\prod_{l>0} \frac{1}{1 - (-q^l)}
		= \sqrt{2} \sqrt{
			\frac{\eta(\tau)}{\theta_2(\tau)}
		}
	$. Therefore, the total contributions from $r$--invariant states are:
	\begin{equation}
		\frac{1}{2}\,Z_{S^1}(\tau)
		+ \abs{\frac{\eta(\tau)}{\theta_2(\tau)}}
	\end{equation}

@@

	The trace can then be computed, following the same recipe as before:
	\begin{equation}
	\begin{aligned}
		\Tr_{S^1} \pqty{
			\frac{1 + r}{2}\,
			q^{L_0 - \tfrac{c}{24}}\,
			\bar{q}^{\tilde{L}_0 - \tfrac{\tilde{c}}{24}}
		}
		&= (q\bar{q})^{
				-\frac{1}{24} + \frac{1}{16}
			}
			\prod_{l + \frac{1}{2} \in \mbb{Z}^+}
			\sum_{N_l,\tilde{N}_l = 0}^\infty
				\frac{1 + (−1)^{N_l + \tilde{N}_l}}{2}\,
				q^{l\cdot N_l}
				\bar{q}^{\,l\cdot \tilde{N}_l} \times 2 \\
		&= \frac{1}{2}\,(q\bar{q})^{+\frac{1}{48}}
		\Bqty{\,
			\prod_{l>0}
				\abs{\frac{1}{1 - q^{l - \frac{1}{2}}}}^2
			+ \prod_{l>0}
				\abs{\frac{1}{1 + q^{l - \frac{1}{2}}}}^2
		}\times 2 \\
		&= \abs{\frac{\eta(\tau)}{\theta_4(\tau)}}
			+ \abs{\frac{\eta(\tau)}{\theta_3(\tau)}}
	\end{aligned}
	\end{equation}
	There is an extra factor of 2 from the number of twisted sectors: $x = 0$ and $x = \pi R$.

@@

	\item \textbf{Torus 4-point function in $bc$ CFT}
	\begin{equation}
		\ave[\big]{
			c(w_1)\,b(w_2)\,
			\tilde{c}(\bar{w}_3)\,\tilde{b}(\bar{w}_4)
		}
		= \int \DD b\,\DD \tilde{b}\,
				\DD c\,\DD \tilde{c}\ %
			c(w_1)\,b(w_2)\,
			\tilde{c}(\bar{w}_3)\,\tilde{b}(\bar{w}_4)\,
			e^{-S'}
		\equiv Z'
	\end{equation}
	First we argue that only the zero modes of the insertions survive the path integral\footnote{
		I would like to thank \textit{谷夏} for some very helpful discussions about this problem.
	}. In fact, as anti-commuting replacements of the gauge degrees of freedom, ghost modes are \textit{defined} to be the eigenvalues of $P^\dagger P$, where $P$ is the conformal Killing differential\footnote{
		Reference: \textit{Polchinski}, Chapter 3 \& 5. 
	}. 
	More specifically, given a conformal Killing vector (CKV) $\var{\sigma^a}$, the conformal Killing equation can be written as:
	\begin{equation}
		P \var{\sigma} = 0
	\end{equation}
	While $P^\dagger \var'\! g = 0$ gives moduli variation $\var'\! g_{ab}$ of the metric. Roughly speaking, $P$ captures the variation of gauge fixing under an arbitrary gauge transformation; naturally, CKV's are given by $(\ker P)$, while $(\det P) \sim \Delta_{FP}$ is the Faddeev--Popov functional measure near the gauge slice. $(\det P)$ can then be calculated with:
	\begin{gather}
		\var{\sigma^a} \mapsto c^a,\quad
		\var'\! g_{ab} \mapsto b_{ab},\quad
		\Delta_{FP}
		\sim \det P
		\sim \int \DD b\,\DD \tilde{b}\,
				\DD c\,\DD \tilde{c}\ e^{-S'},\\
		S'
		= \frac{1}{2\pi} \int \dd[2]{\sigma}
			g^{1/2}\, b_{ab}\,(P\cdot c)^{ab}
		= \frac{1}{2\pi} \int \dd[2]{w}
			\pqty\big{
				b\,\pdbar_w c
				+ \tilde{b}\,\pd_w \tilde{c}
			}
	\end{gather}
	In the end we have chosen conformal gauge, such that\footnote{
		References:
		\begin{itemize}[
			labelindent=3em,labelsep=1pt,
			topsep=.1\baselineskip
		]
		\item Nakahara, \textit{Geometry, Topology and Physics}; 
		\item Blumenhagen et al, \textit{Basic Concepts of String Theory}. 
		\end{itemize}
	} $
		P \sim (\pdbar_w, \pd_w),\ %
		P^\dagger P \sim -\pdbar_w\pd_w = -\laplacian
	$. In the $w = \sigma^1 + i\sigma^2$ coordinates, CKV's are simple translations: $c^a = \mrm{const}$; with $z = e^{-iw}$, it gets mapped to $
		c^z
		= c^w \,\pd_w z
		= c^w \,(-iz)
	$, which agrees with the zero mode $c_0$ in the $c(z)$ expansion:
	\begin{equation}
		c(z)
		= \sum_{m = -\infty}^\infty
			\frac{c_m}{z^{m + 1 - \lambda}}
		= c_0\,z + \sum_{m \ne 0}
			\frac{c_m}{z^{m - 1}}
		,\quad \lambda = 2
		\label{eq:cghost_holomorphic}
	\end{equation}

	Now we are finally ready to prove our argument: for anti-commuting variables like $c(z)$, 
	\begin{equation}
		\int \DD{c}
		\sim \prod_m \int \dd{c_m}
		\sim \prod_m \pdv{c_m}
	\end{equation}
	Since $c_0$ corresponds to a CKV, $P \cdot c_0 = 0$, therefore it vanishes in $S' = \int \dd[2]{\sigma}\pqty{b\cdot P\cdot c}$; for the path integral to be non-zero, there has to be some additional $c_0$ insertions, i.e.
	\begin{equation}
		Z'
		\sim \int \DD b\,\DD \tilde{b}\,
				\DD c\,\DD \tilde{c}\ %
			c_0 b_0
			\tilde{c}_0 \tilde{b}_0\,
			e^{-S'}
		\sim \pqty{\frac{1}{\sqrt{\tau_2}}}^{\!\!4}\!\!
			\int \DD' b\,\DD' \tilde{b}\,
				\DD' c\,\DD' \tilde{c}\ %
			e^{-S'},\quad
		\int \DD' c
		\sim \prod_{m\ne 0} \int \dd{c_m}
	\end{equation}

>>>>

%%% ID: sensitive, do NOT publish!
%\InputIfFileExists{../id.tex}{}{}

\newcommand{\zbar}{\bar{z}}

@@

	Note that here we are working in the grand canonical ensemble, where we have temperature $\beta = 2\pi\tau_2$ and chemical potential $2\pi\tau_1$. At this stage $P$ is \textit{not} fixed, and we should sum over all states with various $P$. To go to the canonical ensemble, we do a Legendre transform and trade $\tau_1$ for some $P_0$. This is implemented by a Laplace / Fourier transform $\int \dd{\tau_1} e^{-i\,(2\pi\tau_1) P_0}$ of the partition function.

	In string theory, we should actually work with the canonical ensemble (and eventually, the \textit{micro-}canonical ensemble), since we would like to impose the \textit{level matching condition}, namely $P_0 = 0$.

	However, in string theory, the Legendre transform is implicit as we integrate along $\tau_1$ in the moduli space; roughly speaking, we have:
	\begin{equation}
		\int \dd{\tau_1} e^{-i\,(2\pi\tau_1) (P - 0)}
		\propto \delta(P - 0)
	\end{equation}
	As $\tau_1$ gets integrated out, we are effectively computing $\Tr' e^{-\beta H}$ where the trace only goes over the $P = 0$ sector of the Hilbert space\footnote{
		This is nicely explained in David Tong's \href{https://www.damtp.cam.ac.uk/user/tong/string.html}{\textit{String Theory}}. See also section 6.3 of Blumenhagen et al, \textit{Basic Concepts of String Theory}. 
	}.

	On the other hand, since we are computing the grand partition function $Z(\tau_1 + i\tau_2)$ for now, we should \textit{not} impose the level matching condition, and the sum should go over all states with various $P$, although this is a much larger Hilbert space than the physical $P = 0$ subspace in string theory.

	Using the expressions in (a), we find that $L_0$ action on a state $\ket{\psi}$ created by $\alpha_{-l},\tilde{\alpha}_{-l}$ yields the sum of occupation number $N_l$ weighted by $l$:
	\begin{equation}
		L_0 \ket{\psi}
		= \pqty{
				\frac{\alpha'k_L^2}{4}
				+ \sum_{l > 0} l\cdot N_l
			} \ket{\psi}
	\end{equation}
	With $c = \tilde{c} = 1$, we obtain:
	\begin{equation}
	\begin{aligned}
		Z(\tau)
		&= (q\bar{q})^{-\frac{1}{24}}
			\sum_{n,w}
				e^{
					- 2\pi \tau_2
					\alpha'\frac{k_L^2 + k_R^2}{4}
				}
				e^{
					2\pi i \tau_1
					\alpha'\frac{k_L^2 - k_R^2}{4}
				}
			\sum_{(N_l),(\tilde{N}_l)}
				q^{
					\,\sum\limits_{l>0}  l\cdot N_l
				}
				\bar{q}^{
					\,\sum\limits_{l>0}  l\cdot \tilde{N}_l
				} \\
		&= (q\bar{q})^{-\frac{1}{24}}
			\sum_{n,w}
				e^{
					- \pi \tau_2 \pqty{
						\frac{\alpha'n^2}{R^2}
						+ \frac{w^2 R^2}{\alpha'}
					}
					+ 2\pi i \tau_1 nw
				}
			\sum_{(N_l),(\tilde{N}_l)} \prod_{l>0}
				q^{l\cdot N_l}
				\bar{q}^{\,l\cdot \tilde{N}_l} \\
		&= \abs{\eta(\tau)}^{-2}
			\sum_{n,w}
				e^{
					- \pi \tau_2 \pqty{
						\frac{\alpha'n^2}{R^2}
						+ \frac{w^2 R^2}{\alpha'}
					}
					+ 2\pi i \tau_1 nw
				}
	\end{aligned}
	\end{equation}
	We've simplified the contributions from the oscillator modes using $\eta(\tau)$, since they are identical to the oscillator contributions of the non-compact $X\in\mbb{R}^1$:
	\begin{equation}
	\begin{aligned}
		(q\bar{q})^{-\frac{1}{24}}\!\!\!\!\!
		\sum_{(N_l),(\tilde{N}_l)} \prod_{l>0}
			q^{l\cdot N_l}
			\bar{q}^{\,l\cdot \tilde{N}_l}
		&= (q\bar{q})^{-\frac{1}{24}}
			\prod_{l>0} \sum_{N_l,\tilde{N}_l = 0}^\infty
				q^{l\cdot N_l}
				\bar{q}^{\,l\cdot \tilde{N}_l} \\
		&= (q\bar{q})^{-\frac{1}{24}}
			\prod_{l>0}
				\frac{1}{1 - q^l}
				\frac{1}{1 - \bar{q}^{\,l}}
		= \abs{\eta(\tau)}^{-2}
	\end{aligned}
	\end{equation}

@@

	The sum, on the other hand, is naturally invariant under $T\colon \tau \mapsto \tau + 1$, by making a change of variables $m \mapsto m + w$. It is also invariant under $S\colon \tau \mapsto -1/\tau$ with $m \mapsto -w, w \mapsto m$\,\footnote{
		Reference: \textit{Polchinski}. 
	}. Therefore, $Z(\tau)$ is modular invariant.

@@

	For the second term, note that:
	\begin{equation}
		r\colon\ %
				\ket{(N_l),(\tilde{N}_l);n,w}
			\longmapsto (-1)^{\sum_l (N_l + \tilde{N}_l)}
				\ket{(N_l),(\tilde{N}_l);-n,-w}
	\end{equation}
	In particular, it reverses $n,w$, hence $r$ insertion gives vanishing amplitude unless $n = w = 0$; the summation is very much similar to the $Z_{S^1}$ case, i.e. we have:
	\begin{equation}
	\begin{aligned}
		\frac{1}{2} \Tr_{S^1} \pqty\Big{
			r\,
			q^{L_0 - \tfrac{c}{24}}\,
			\bar{q}^{\tilde{L}_0 - \tfrac{\tilde{c}}{24}}
		}
		&= \frac{1}{2}\,(q\bar{q})^{-\frac{1}{24}}
			\prod_{l>0} \sum_{N_l,\tilde{N}_l = 0}^\infty
				(-1)^{N_l + \tilde{N}_l}
				q^{l\cdot N_l}
				\bar{q}^{\,l\cdot \tilde{N}_l} \\
		&= \frac{1}{2}\,(q\bar{q})^{-\frac{1}{24}}
			\prod_{l>0}
				\frac{1}{1 - (-q^l)}
				\frac{1}{1 - (-\bar{q}^{\,l})}
		= \abs{\frac{\eta(\tau)}{\theta_2(\tau)}}
	\end{aligned}
	\end{equation}
	Where we've used the fact that\footnote{
		Reference: Blumenhagen \& Plauschinn, \textit{Introduction to CFT}, and also \textit{Polchinski}. 
	}: $
		q^{-\frac{1}{24}}
		\prod_{l>0} \frac{1}{1 - (-q^l)}
		= \sqrt{2} \sqrt{
			\frac{\eta(\tau)}{\theta_2(\tau)}
		}
	$. Therefore, the total contributions from $r$--invariant states are:
	\begin{equation}
		\frac{1}{2}\,Z_{S^1}(\tau)
		+ \abs{\frac{\eta(\tau)}{\theta_2(\tau)}}
	\end{equation}

@@

	The trace can then be computed, following the same recipe as before:
	\begin{equation}
	\begin{aligned}
		\Tr_{S^1} \pqty{
			\frac{1 + r}{2}\,
			q^{L_0 - \tfrac{c}{24}}\,
			\bar{q}^{\tilde{L}_0 - \tfrac{\tilde{c}}{24}}
		}
		&= (q\bar{q})^{
				-\frac{1}{24} + \frac{1}{16}
			}
			\prod_{l + \frac{1}{2} \in \mbb{Z}^+}
			\sum_{N_l,\tilde{N}_l = 0}^\infty
				\frac{1 + (-1)^{N_l + \tilde{N}_l}}{2}\,
				q^{l\cdot N_l}
				\bar{q}^{\,l\cdot \tilde{N}_l} \times 2 \\
		&= \frac{1}{2}\,(q\bar{q})^{+\frac{1}{48}}
		\Bqty{\,
			\prod_{l>0}
				\abs{\frac{1}{1 - q^{l - \frac{1}{2}}}}^2
			+ \prod_{l>0}
				\abs{\frac{1}{1 + q^{l - \frac{1}{2}}}}^2
		}\times 2 \\
		&= \abs{\frac{\eta(\tau)}{\theta_4(\tau)}}
			+ \abs{\frac{\eta(\tau)}{\theta_3(\tau)}}
	\end{aligned}
	\end{equation}
	There is an extra factor of 2 from the number of twisted sectors: $x = 0$ and $x = \pi R$.

@@

	\item \textbf{Torus 4-point function in $bc$ CFT}
	\begin{equation}
		\ave[\big]{
			c(w_1)\,b(w_2)\,
			\tilde{c}(\bar{w}_3)\,\tilde{b}(\bar{w}_4)
		}
		= \int \DD{b} \DD{\tilde{b}}
				\DD{c} \DD{\tilde{c}}\,
			c(w_1)\,b(w_2)\,
			\tilde{c}(\bar{w}_3)\,\tilde{b}(\bar{w}_4)\,
			e^{-S'}
		\equiv Z'
	\end{equation}
	First we argue that only the zero modes of the insertions survive the path integral\footnote{
		I would like to thank \textit{谷夏} for some very helpful discussions about this problem.
	}. In fact, as anti-commuting replacements of the gauge degrees of freedom, ghost modes are \textit{defined} to be the eigenvalues of $P^\dagger P$, where $P$ is the conformal Killing differential\footnote{
		Reference: \textit{Polchinski}, Chapter 3 \& 5. 
	}. 
	More specifically, given a conformal Killing vector (CKV) $\var{\sigma^a}$, the conformal Killing equation can be written as:
	\begin{equation}
		P \var{\sigma} = 0
	\end{equation}
	While $P^\dagger \var'\! g = 0$ gives moduli variation $\var'\! g_{ab}$ of the metric. Roughly speaking, $P$ captures the variation of gauge fixing under an arbitrary gauge transformation; naturally, CKV's are given by $(\ker P)$, while $(\det P) \sim \Delta_{FP}$ is the Faddeev--Popov functional measure near the gauge slice. $(\det P)$ can then be calculated with:
	\begin{gather}
		\var{\sigma^a} \mapsto c^a,\quad
		\var'\! g_{ab} \mapsto b_{ab},\quad
		\Delta_{FP}
		\sim \det P
		\sim \int \DD{b} \DD{\tilde{b}}
				\DD{c} \DD{\tilde{c}} e^{-S'},\\
		S'
		= \frac{1}{2\pi} \int \dd[2]{\sigma}
			g^{1/2}\, b_{ab}\,(P\cdot c)^{ab}
		= \frac{1}{2\pi} \int \dd[2]{w}
			\pqty\big{
				b\,\pdbar_w c
				+ \tilde{b}\,\pd_w \tilde{c}
			}
	\end{gather}
	In the end we have chosen conformal gauge, such that\footnote{
		References:
		\begin{itemize}[
			labelindent=3em,labelsep=1pt,
			topsep=.1\baselineskip
		]
		\item Nakahara, \textit{Geometry, Topology and Physics}; 
		\item Blumenhagen et al, \textit{Basic Concepts of String Theory}. 
		\end{itemize}
	} $
		P \sim (\pdbar_w, \pd_w),\ %
		P^\dagger P \sim -\pdbar_w\pd_w = -\laplacian
	$. In the $w = \sigma^1 + i\sigma^2$ coordinates, CKV's are simple translations: $c^a = \mrm{const}$; with $z = e^{-iw}$, it gets mapped to $
		c^z
		= c^w \,\pd_w z
		= c^w \,(-iz)
	$, which agrees with the zero mode $c_0$ in the $c(z)$ expansion:
	\begin{equation}
		c(z)
		= \sum_{m = -\infty}^\infty
			\frac{c_m}{z^{m + 1 - \lambda}}
		= c_0\,z + \sum_{m \ne 0}
			\frac{c_m}{z^{m - 1}}
		,\quad \lambda = 2
		\label{eq:cghost_holomorphic}
	\end{equation}

	Now we are finally ready to prove our argument: for anti-commuting variables like $c(z)$, 
	\begin{equation}
		\int \DD{c}
		\sim \prod_m \int \dd{c_m}
		\sim \prod_m \pdv{c_m}
	\end{equation}
	Since $c_0$ corresponds to a CKV, $P \cdot c_0 = 0$, therefore it vanishes in $S' = \int \dd[2]{\sigma}\pqty{b\cdot P\cdot c}$; for the path integral to be non-zero, there has to be some additional $c_0$ insertions, i.e.
	\begin{equation}
		Z'
		\sim \int \DD{b} \DD{\tilde{b}}
				\DD{c} \DD{\tilde{c}}\,
			c_0 b_0
			\tilde{c}_0 \tilde{b}_0\,
			e^{-S'}
		\sim \pqty{\frac{1}{\sqrt{\tau_2}}}^{\!\!4}\!\!
			\int \DD{'b} \DD{'\tilde{b}}
				\DD{'c} \DD{'\tilde{c}}\,
			e^{-S'},\quad
		\int \DD{'c}
		\sim \prod_{m\ne 0} \int \dd{c_m}
	\end{equation}

### 2021-06-09 alpha/Ising/ising.tex
Add comments on string partition function & more

	Some choose to call this the \textit{quantum--classical correspondence}\footnote{
		See \cite{Simmons-Duffin:2016gjk} and \url{https://mcgreevy.physics.ucsd.edu/s19/2019-215C-lectures.pdf}. 
	}. Here we shall take the second perspective, and the Hilbert space consists of the 2-component Pauli spinor $s(x)$ located at each site~$x$.

>>>>

	Some choose to call this the \textit{quantum--classical correspondence}\footnote{
		See \cite{Simmons-Duffin:2016gjk} and \https{mcgreevy.physics.ucsd.edu/s19/2019-215C-lectures.pdf}, and also \href{https://mcgreevy.physics.ucsd.edu/s14/239a-lectures.pdf}{\texttt{/s14/239a-lectures.pdf}}. 
	}. Here we shall take the second perspective, and the Hilbert space consists of the 2-component Pauli spinor $s(x)$ located at each site~$x$.
